---
title: "The Grammar of Graphics (of ggplot2)"
author: "Lucas Mello Schnorr, Jean-Marc Vincent"
date: "February 14, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a demonstration of how ggplot works.

An empty plot: understanding the layered nature of ggplot.

```{r}
library(ggplot2);
ggplot();
```

There is no data plot yet. Let's use the **pressure** data set:

```{r}
pressure;
```

Let's plot the simplest case, just points and a line interpolating them.

```{r}
ggplot(data=pressure, aes(x=temperature, y=pressure)) + geom_point() + geom_line();
```

How to customize labels:

```{r}
ggplot(data=pressure, aes(x=temperature, y=pressure)) +
    geom_point() +
    geom_line() +
    xlab("Temperature (deg C)") +
    ylab("Pressure (mm of Hg)");
```

We can associate the size and color of points to other variables.

```{r}
ggplot(data=mtcars, aes(x=disp, y=hp, size=mpg, color=wt)) + 
  geom_point();
```

Let's see the list of all aesthetics accepted by **geom_point()**:
http://docs.ggplot2.org/current/geom_point.html

Let's plot a histogram:

```{r}
str(cars);
```


```{r}
cars;
```

```{r}
ggplot(data=cars) +
  geom_histogram(aes(x=dist));
```

Merge a histogram and the corresponding Probability Density Function (PDF).

```{r}
ggplot(cars, aes(x=dist)) +
  geom_histogram(binwidth = 10,color='blue')+
  geom_density(aes(y=10 * ..count..),color='red');
```

Boxplot of speed, using a point to represent the mean value.
```{r, fig.width=3, fig.height=5}
ggplot(cars, aes(x=1, y=speed)) + geom_boxplot() + geom_point(y=mean(cars$speed));
```

Using facets to separate data.

```{r}
ggplot(mtcars, aes(x=hp, y=mpg)) + facet_wrap(~gear) + geom_point();
```
```{r}
nileData <-  read.csv("data/Nile.csv");
nileData;
```
```{r}
ggplot(data=nileData)+ geom_point(aes(x=time,y=Nile,color=Nile));
```

```{r}
ggplot(data=nileData)+ geom_histogram(aes(x=Nile));
```


Ce graphique représente le nombre d'effectifs par rapport à la hauteur du Nil.

```{r}
ggplot(data=nileData)+ geom_polygon(aes(x=time,y=Nile,color=Nile))
```


